A Fast Unified Model for Parsing and Sentence Understanding

### 2016-03-18 writing/hard_stack_paper/paper.tex
Make the speed claim as strong as possible here, too

We evaluate SPINN on the Stanford Natural Language Inference entailment task \citep[SNLI,][]{snli:emnlp2015}, and find that it significantly outperforms other sentence encoding-based models, and that it yields speed increases of over 10x over a standard TreeRNN implementation.

>>>>

We evaluate SPINN on the Stanford Natural Language Inference entailment task \citep[SNLI,][]{snli:emnlp2015}, and find that it significantly outperforms other sentence encoding-based models, and that it yields speed increases of up to 25x over a standard TreeRNN implementation.
